%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%% Content starts here %%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Problem 1}
\begin{scriptsize}
Given array $A = { a_i }$, where $0 <= i < n$, from integers (size end the elements) read from SI.
Write a program that will form new array $B = { b_i }$, where $0 <= i < \frac{n}{2}$ if n is even, or 
$0 <= i < \frac{n}{2} + 1$ if $n$ is odd, so $b_0 = $ sum of digits of odd positions of number $a_0 = $ sum of digits on even positions of number $a_n-1$. Print the array $b$ on SO.
The least significant digit is on position 1. 

\textbf{The sum of digits on even or odd positions should be computed
in a separate recursive functions (or one function).}
\end{scriptsize}
\end{frame}

\begin{frame}[fragile]{Problem 1}{Solution}
\lstinputlisting{src/av11/p111.c}
\end{frame}

\begin{frame}{Problem 2}
Given a square matrix (the size and the elements are read from SI).
Write a program that will print ond SO "YES" if the sum of elements that are at 
the same time over the main and under the supportive diagonal and under the main and over the
supportive is larger than the sum of
the elements at the same time under the main and under the supportive diagonal and over the main and over
the supportive. In the oposite case print "NO".
\end{frame}

\begin{frame}[fragile]{Problem 2}{Solution 1/2}
\lstinputlisting[lastline=22]{src/av11/p112.c}
\end{frame}

\begin{frame}[fragile]{Problem 2}{Solution 2/2}
\lstinputlisting[firstline=23]{src/av11/p112.c}
\end{frame}

\begin{frame}{Problem 3}
Given a text file with name "text.txt". Write a program that will print 
how many rows have less then average words per row. In the file the words are composed only of alphanumerical characters and
the max size of a row is 80. Print the result on the SO.
\end{frame}

\begin{frame}[fragile]{Problem 3}{Solution 1/2}
\lstinputlisting[lastline=16]{src/av11/p113.c}
\end{frame}

\begin{frame}[fragile]{Problem 3}{Solution 2/2}
\lstinputlisting[firstline=17]{src/av11/p113.c}
\end{frame}

