%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%% Content starts here %%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}[fragile]{Problem 1}
\begin{tiny}
The Skopje theater desided to introduce system that for each visitor will
generate unique threedigit number. This number determines the type of the
visitor, so if the first digit is:
\begin{itemize}
  \item 1, it's VIP visitor
  \item 2 - 9, regular visitor  
\end{itemize}

The entrance number is determined by the residue of the number division by 3.
If the residue is: 
\begin{itemize}
  \item 0, it's first entrance
  \item 1, it's second entrance
  \item 2, it's third entrance.  
\end{itemize}
Your task is to write a program that will read number from SI and print the kind
of the visitor and it's entrance number. If the number is not threedigit
apropriate message should be printed.


\emph{Example}:
\begin{verbatim}
	Input:				Output:
    135				    VIP visitor at entrance 1
\end{verbatim}
\end{tiny}

\end{frame}

\begin{frame}[fragile]{Problem 1}{Solution}
\lstinputlisting{src/kol/p1.c}
\end{frame}

\begin{frame}[fragile]{Problem 2}
Write a program that will read characters from SI while the character '.' is
read. Than the program should print on the standard output the character with
most consecutive occurances. If there are more characters with same number of
consecutive occurances, print the first of them.\emph{Example:}
\begin{verbatim}
	Input:				
		ova-Treba da Elesnaaaaa_zAaaadddddacca.
	Output: 
		a 5
\end{verbatim}
\end{frame}
\begin{frame}[fragile,shrink=.95]{Problem 2}{Solution}
\lstinputlisting{src/kol/p2.c}
\end{frame}


\begin{frame}[fragile]{Problem 3}
\begin{tiny}
In the national football league are participating \texttt{n} (\texttt{n > 2})
teams. Each team plays 2 games (home and away) with each of remainding teams.
The winning team gets 3 points, and the defeated 0. In case of draw, two teams
earn 1 point. Write a program that will read one natural number \texttt{n} - the
number of teams, and then information about wins, draws and losses of \textbf{n}
teams after the end of the league. The program should output maximum number of
points won by a team, and the ordinal number of the team (the first team has
number 1, second 2, etc.). Also, if the maximum number of points is more than
75\% of maximum available points, the program should output \texttt{``Great
season''}, otherwise \texttt{``Bad season''}.
\emph{Example:}
\begin{verbatim}
	Input:				Output:
	6               Maximum points: 23
	6   3   1	    Ordinal number: 3
	2   2   6	    Great season
	7   2   1
	0   0   10
	4   3   3
	5   2   3
\end{verbatim}
\end{tiny}
\end{frame}

\begin{frame}[fragile]{Problem 3}{Solution}
\lstinputlisting{src/kol/p3.c}
\end{frame}

\begin{frame}[fragile]{Problem 4}
Write a program that will read one natural number \texttt{n} and will print the
smallest ``hapy'' number greater than \texttt{n}. We say that number is
``happy'' if it contains only ``happy'' digits (7 and 9).

Example:
\begin{verbatim}
	Input:			Output:
	789				797
\end{verbatim}

\end{frame}

\begin{frame}[fragile]{Problem 4}{Solution}
\lstinputlisting{src/kol/p4.c}
\end{frame}

\begin{frame}[fragile]{Problem 5}
Write a program that will check numbers from 1 to 100 and for each number
divisible by 3 instead of the number will print \texttt{``Fizz''}, and for each
number divisible by 5 instead of the number will print \texttt{``Buzz''}.
Instead of numbers divisible by 3 and 5 will print \texttt{``FizzBuzz''}.
\end{frame}

\begin{frame}[fragile]{Problem 5}{Solution}
\lstinputlisting{src/kol/p5.c}
\end{frame}
